---
title: "task11.Rmd"
author: "Simona"
date: "November 12, 2016"
output: html_document
---
Lets open a data array longley
```{r}
head(longley)
```
###Lets do the first task.    
Lets evaluate the model of simple linear regression.
```{r}
x <- longley$Employed
y <- longley$GNP
model <- lm(y~x)
summary(model)
```
Explanations:  
Call - function formula;  
Residuals - minimum, first quartile, median, third quartile, maximum;  
Coefficients - estimates of  β0 and β1, standard deviation, t-test value, probability;  
Signif. codes - categories of probability;  
Residual standard error - data standard error;  
Multiple R-squared, Adjusted R-squared - grade of model suitability (max is 1);  
F-statistic - Fischer distribution statistics;  
P-value - probability that the statistical summary would be the same as or more extreme than the actual observed results.  
    
Probability is below 0.05, which indicates that model is statistically significant.

###Lets do the second task.     
Lets make a model forecast at given points.
```{r}
x1 <- c(62, 65, 68)
y1 = predict(model, newdata=data.frame(x=x1))
y1
```
###Lets do the third task.    
Lets make a variable dispersion graph with linear regression line and new forecasts.
```{r}
plot(x, y, xlab='Employed', ylab='GNP')
abline(model, col='blue')
points(x1, y1, col=2, pch=19)
grid()
legend("topleft", c("Data","Regression line", "Forecasts"), lty=c(0,1,0), pch=c(1,NA,19), col=c(1,4,2))
```

Reference <https://github.com/simona1234/Econometrics1/blob/master/task11/task11.Rmd>
