---
title: "task6"
author: "Simona"
date: "October 24, 2016"
output: html_document
---
# Data reading and correction

### Lets read data from csv file
```{r}
df = read.csv('/home/simona/Desktop/R_programing_swirlResults.csv', stringsAsFactors=FALSE)
sapply(df, class) 
```
Lets fix incorrect data
```{r}
df <- transform(df, sysTime = as.POSIXlt(sysTime), datetime = as.POSIXlt(datetime))
```
### Lets delete wrong data ("1vbutkus", "aaa", "testas")
```{r}
unique(df$user)
ind <- with(df, which(user=="aaa" | user=="testas" | user=="1vbutkus"))
df <- df[-ind,]
unique(df$user)
```
Lets eliminate duplicates of names in data (assign it to the same person)
```{r}
df$user[df$user=="gyse"] <- "gyse3054"
df$user[df$user=="rokasalek"] <- "rokasaleks"
df$user[df$user=="Juste" | df$user=="ju" | df$user=="j"] <- "juste"
unique(df$user)
```
Lets eliminate duplicates of lessons in data (7 - username, 9 - lesson, 10 - question, 12 - attempt, 14 - skipped)
```{r}
df2 <- df[,c(7, 9, 10, 12, 14)]
dup <- which(duplicated(df2), TRUE)
df <- df[-dup,]
```

# Data analysis

### Lets answer to some important practical questions
Lets find students who skipped questions
```{r}
ind <- with(df, which(skipped =="TRUE"))
df_skipped <- df[ind,]
users <- unique(df_skipped$user)
users
```
Lets eliminate students who skipped questions
```{r}
ind <- with(df, which(is.element(df$user, users) =="TRUE"))
df_noskip <- df[-ind,]
unique(df_noskip$user)
```
Lets find out how many lessons each student did
```{r}
df_noskip <- df_noskip[,c(7, 9)]
dup <- which(duplicated(df_noskip), TRUE)
df_noskip <- df_noskip[-dup,]
table(df_noskip$user)
```
Students who did all the lessons is: "aipe00", "simona1234", "emru3000", "zagnyte"
Lets find the number of undone lessons
```{r}
ind <- with(df_noskip, which(user=="aipe00" | user=="emru3000" | user=="simona1234" | user=="zagnyte"))
df_noskip <- df_noskip[-ind,]
16-table(df_noskip$user)
```
Lets find out how many questions each student skipped
```{r}
table(df_skipped$user)
```
Lets find which students skipped questions in lessons
```{r}
df_skipped <- unique(df_skipped[c("user", "lesson_name")])
table(head(df_skipped, 10))
```
Lets filter data into two arrays
```{r}
library("knitr")
df_skipped <- unique(df_skipped[c("user", "lesson_name")])
kable(head(df_skipped, 10))
ind <- with(df, which(is.element(df$user, users) =="TRUE"))
df2 <- df[ind,]
df2 <- df2[,c(7, 9)]
dup <- which(duplicated(df2), TRUE)
df2 <- df2[-dup,]
kable(head(df2, 10))
```
Lets find how many lessons is undone by each student
```{r}
16-table(df2$user)+table(df_skipped$user)
```

# Other interesting questions

### Whats the average of time to pass the tasks?
Lets correct the data
```{r}
df_time <- df[,c(3, 6, 7, 9, 13)]
df2 <- df[,c(7,9)]
dup <- which(duplicated(df2), TRUE)
df_time <- df_time[-dup,]
kable(head(df_time))
```
Lets find the real time each student spent
```{r}
real_taketime <- round(difftime(df_time$sysTime, df_time$datetime, units="mins"))
df_time <- cbind(df_time, real_taketime)
kable(head(df_time))
```
Lets find out the average all students spent to do the task
```{r}
lessons <- split(df_time, f=df_time$lesson_name)
time_decl <- sapply(lessons, function(x) round(mean(x$takeTime), 2))
sort(time_decl)
```
### Can we trust declared time?
```{r}
timedif <- abs(df_time$takeTime - df_time$real_taketime)
mean(timedif)
```
### Which tasks were the most difficult?
Lets count the most difficult tasks by declared time
```{r}
head(sort(time_decl, decreasing=TRUE))
```
Reference https://github.com/simona1234/Econometrics1/blob/master/task6/task6.Rmd
