---
title: "task5"
author: "Simona"
date: "October 23, 2016"
output: html_document
---
```{r}
library(prob)
```
Lets generate random variable called S
```{r}
n <- 10^5
S <- replicate(n, sum(sample(1:6, 3, replace=TRUE)))
head(S)
```
Lets find theoretical distribution of S
```{r}
probS <- rolldie(3, nsides = 6, makespace = TRUE)
probS <- addrv(probS, sum = X1 + X2 + X3)
theorS <- marginal(probS, vars="sum")
theorS
```
Lets create a frequency table from a generated sample
```{r}
data <- table(S)/n
cbind(as.data.frame(data),theorS)
```
Lets create a graph from a generated sample
```{r}
plot(data, xlab = "Total", ylab = "Probability", col = "black", lwd = 3)
points(theorS, col = "yellow", lwd = 3)
```
Lets count theoretical expected value and variance of random variable S
```{r}
exval <- sum(theorS$probs * theorS$sum)
exval
varS <- sum(theorS$probs * (theorS$sum - exval)^2)
varS
```
Lets make a graph of expected value converging to theoretical value when n is increasing
```{r}
plot(cumsum(S)/1:n, xlab= "n", ylab = "S/n", ylim = c(10,12), type = "l", main = "Expected value converging to theoretical value", xlim = c(0,700))
abline (h=exval, col = "yellow", lwd = 0.7)
```
Lets make a graph of expected variance converging to theoretical variance when n is increasing
```{r}
a = S*0
for(i in 1:700){
  a[i]=var(S[1:i])
}
plot(a[1:700], type="l", xlab="n", ylab="Expected variance", main = "Expected variance converging to theoretical variance")
abline(h=varS, col = "yellow", lwd = 0.7)
```
Reference <https://github.com/simona1234/Econometrics1/blob/master/task5/task5.Rmd>
